A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-23 0_main.tex
turn off draft hyperref
lil edits

\documentclass[5p,twocolumn,10pt,times]{elsarticle}
\usepackage{amsmath}
\usepackage[draft]{hyperref} % added [draft] to avoid compilation issues that happen if a link is split and appears in two pages
%\modulolinenumbers[5]
\addtolength{\textheight}{8mm}
\addtolength{\textwidth}{4mm}
\addtolength{\voffset}{-10mm}
\addtolength{\hoffset}{-3mm}

@@

\begin{abstract}
3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
FDM builds up objects by depositing material along paths which lie in horizontal layers.
The outlines of each layer are filled using contour-following toolpaths approximately the size of the printing nozzle.
Filling the outlines with extruded material densely is important for fabricating parts with high stiffness and dimensional accuracy.
An accurate dense filling is especially important for thin parts such as casings for electronics, blowmolding prototypes, (architectural) models, and microstructures.

>>>>

\documentclass[5p,twocolumn,10pt,times]{elsarticle}
\usepackage{amsmath}
\usepackage{hyperref} % added [draft] to avoid compilation issues that happen if a link is split and appears in two pages
%\modulolinenumbers[5]
\addtolength{\textheight}{8mm}
\addtolength{\textwidth}{4mm}
\addtolength{\voffset}{-10mm}
\addtolength{\hoffset}{-3mm}

@@

\begin{abstract}
3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
FDM builds up objects by depositing material along toolpaths which lie in horizontal layers.
The outlines of each layer are filled using contour-following toolpaths approximately the size of the printing nozzle.
Filling the outlines with extruded material densely is important for fabricating parts with high stiffness and dimensional accuracy.
An accurate dense filling is especially important for thin parts such as casings for electronics, blowmolding prototypes, (architectural) models, and microstructures.

### 2019-08-23 1_intro.tex
lil edits

FDM printers extrude semi-continuous beads of molten plastic through a nozzle, which moves along a planned toolpath within each layer of a 3D object.
Because the resolution of the positioning system is order of magnitude smaller than the width of the nozzle (typically from $??$ to $??$),
the toolpaths for filling the arbitrary polygonal shape of a layer with extrusion beads are following the contour of that layer.
\jun{I had difficulty to follow the logic behind this sentence}

>>>>

FDM printers extrude semi-continuous beads of molten plastic through a nozzle, which moves along a planned toolpath within each layer of a 3D object.
A common strategy to accurately manufacture a given 3D model is to extrude a contour following print path,
because the positiong and shape of the toolpath can be controled relatively accurately.
Filling up a shape using parallel straight lines would expose defects of the size of the nozzle ($\pm 10^2 \mu$), which is generally an order of magnitude larger than the resolution of the positioning system ($\pm 10^1 \mu$).
Contour parallel extrusion therefore leads to a less bumpy outline shape than direction parallel extrusion does.

### 2019-08-23 4_method.tex
lil edits

We mark a node of the skeleton as central if its feature radius is larger than that of all of the neighboring nodes in the skeletal graph.
That is: we mark the local maxima, i.e. the mountain tops of the UoC as being central.
We also mark whole bones as being central if they are significant according to a common significance measure.

\subsubsection{Significance measure}\label{sec:significance_measure}
Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the angle $\angle{p_ovp_1}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
Bones are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading strategy.

>>>>

We mark a node of the skeleton as central if its feature radius is larger than that of all of the neighboring nodes in the skeletal graph.
That is: we mark the local maxima, i.e. the mountain tops of the UoC as being central.
We also mark whole bones as being central if they are significant according to a significance measure which is commonly used in shape analysis.

\subsubsection{Significance measure}\label{sec:significance_measure}
Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the interior angle $\angle{p_ovp_1} \leq \si{180}{\degree}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
Bones are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading strategy.
